Spin canonical rings of log stacky curves

### 2015-07-02 stacky_write_up/spin_cring.tex
change title divisor -> ring, minor intro edits

\title{Spin canonical divisors of log stacky curves}

@@

\begin{defn}
\label{defn:divisor-floor}
If Weil divisor $D \in \di \sx$ and $D = \sum_{i = 1}^{n} \alpha_i P_i$
with $\alpha_i \in \BQ$, the floor of a divisor $\lfloor D
\rfloor$ is defined to be $\lfloor D \rfloor := \sum_{i = 1}^{n}
\lfloor \alpha_i \rfloor P_i$.
\end{defn}

A pair of a stacky curve and a log divisor $(\sx, \Delta)$ is called a \textbf{log stacky curves}
and the study of their canonical rings is the main focus of
the work by Voight and Zureick-Brown \cite{vzb:stacky}.
For this paper, we consider \textbf{log spin curves} which are
triples $(\sx, \Delta, \halfcan)$ where $\sx$ is a stacky curve, $\Delta$ is a log divisor, and $\halfcan \in \di \sx$ satisfies
$2\halfcan \sim K_X + \Delta + \sum_{i=1}^{r}\frac{e_i-1}{e_i}P_i$. Such a divisor $\halfcan$
is called a \textbf{log spin canonical divisor} on $(\sx, \Delta)$. 
We use $\halfcan_X := \lfloor L \rfloor $ to refer to the spin canonical divisor
(also known as the half-canonical divisor, semi-canonical divisor, 
or theta characteristic) associated to the
coarse space $X$ of $\sx$, i.e. $\halfcan_X$ is a divisor such
that $2\halfcan_X \sim K_X + \Delta$. Furthermore, we use the following
analogous notation:

>>>>

\title{Spin canonical rings of log stacky curves}

@@

\begin{defn}
\label{defn:divisor-floor}
If divisor $D \in \di \sx$ and $D = \sum_{i = 1}^{n} \alpha_i P_i$
with $\alpha_i \in \BQ$, the floor of a divisor $\lfloor D
\rfloor$ is defined to be $\lfloor D \rfloor := \sum_{i = 1}^{n}
\lfloor \alpha_i \rfloor P_i$.
\end{defn}

A pair of a stacky curve and a log divisor $(\sx, \Delta)$ is
called a \textbf{log stacky curves} and the study of their
canonical rings is the main focus of the work by Voight and Zureick-
Brown \cite{vzb:stacky}. For this paper, we consider \textbf{log
spin curves} which are triples $(\sx, \Delta, \halfcan)$ where $\sx$
is a stacky curve, $\Delta$ is a log divisor, and $\halfcan \in \di
\sx$ satisfies $2 \halfcan \sim K_X + \Delta + \sum_{i = 1}^{r}
\frac{e_i - 1}{e_i} P_i$. Such a divisor $\halfcan$ is called a
\textbf{log spin canonical divisor} on $(\sx, \Delta)$. We use
$\halfcan_X := \lfloor L \rfloor $ to refer to the \textbf{spin
canonical divisor} (also known as the half-canonical divisor, semi-
canonical divisor, or theta characteristic) associated to the
coarse space $X$ of $\sx$  (i.e. $\halfcan_X$ is a divisor such
that $2\halfcan_X \sim K_X + \Delta$). Furthermore, we use the
following analogous notation:
